Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-27 2017-Xudong-SMT/OpenPNets-SMT.tex
structure

\ERIC{imported from FORTE'16, }

@@

\paragraph{Structure.}

\section{Running Examples}
Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
many examples of pNets, encoding
operators of various classical process algebras, or more complex
synchronisation structures in distributed or parallel languages.
In this section, we use two process expressions, respectively from CCS
and from Lotos, to illustrate different features of pNets. They will
serve as running examples in the whole paper.

@@

\section{Implementation}
The VerCors platform uses (closed) pNets as the intermediate language
for some high-level language or graphical formalism to be translated
into both input for a 
model-checker and for generating executable code automatically \cite{HKM-FASE16}.
% to ease the
% specification from non-expert users, compiling it
%from those language or graphical formalism in the pNet API.

@@

\TODO{Option: Add the process and the vector ids ?}

>>>>

@@

\TODO{say that apart from the old work by J. Rathke, we know no other
  research addressing our goals, and especially no attempts to develop
  an algorithmic treatment of such symbolic systems by interacting
  with automatic theorem provers}.

\TODO{Then you can list the ATP/ITP you have mentionned Coq, Isabelle,
  B-tools, or others like CVC4, as possible alternative to Z3}

\paragraph{Structure.}
In \ref{section:examples} we present two simple examples taht will be
running examples to illustrate all parts of the paper. Then in the
background section
\ref{section:pnets} we give a description and a formal definition of
the pNet model, as found in previous publications.
Section \ref{section:op-semantics} recalls the operationnal semantics
of pNet, including its structural rules, and a sketch of the algorithm
to compute such semantics, but also explains the enhancment we have
done to these definitions.
Section \ref{section:implementation} explains in details our
implementation within the Vercors plateform, and shows the full result of
the semantic computation on one of the running examples.
Finally we conclude and discuss perspectives in section
\ref{section:conclusion}.

\section{Running Examples}
\label{section:examples}

Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
many examples of pNets, encoding
operators of various classical process algebras, or more complex
synchronisation structures in distributed or parallel languages.
In this section, we use two process expressions, respectively from CCS
and from Lotos, to illustrate different features of pNets. They will
serve as running examples in the whole paper.

@@

\section{Implementation}
\label{section:implementation}
The VerCors platform uses (closed) pNets as the intermediate language
for some high-level language or graphical formalism to be translated
into both input for a 
model-checker and for generating executable code automatically \cite{HKM-FASE16}.
% to ease the
% specification from non-expert users, compiling it
%from those language or graphical formalism in the pNet API.

@@

%\TODO{Option: Add the process and the vector ids ?}
